Vagueness and imprecise imitation in signaling games

### 2016-02-22 paper/version_05/paper.tex

Imitation of success, as described above, presupposes that agents make no mistakes when
observing states, or choosing interpretations. This may not always be an appropriate
assumption, especially when some states can be perceptually similar and therefore likely to be
confused for one another. Therefore, imitation dynamics could be affected by at least two
sources of probabilistic noise:

>>>>

Imitation of success, as described above, presupposes that agents make no mistakes when
observing states, or choosing interpretations. This may not always be an appropriate
assumption, especially when some states can be perceptually similar and therefore likely to be
confused for one another.
Human performance in these situations has been studied by a number of authors in experimental psychology~\citep{takane_structures_1992}.
In a stimulus identification experiment~\citep{luce_detection_1963}, subjects are presented in each trial with a stimulus to be identified out of a fixed set.
The more similar the stimuli are to each other, the larger the number of errors subjects make.
For example, in Robert Nosofsky's experiments~\citep{Nosofsky1986:Attention-Simil}, stimuli consisted of 16 semicircles with a radial line from the center to the rim, varying in size (radius of 0.478, 0.500, 0.522, or 0.544 cm) and angle of the line (50º, 53º, 56º, or 59º).
In over 9000 trials, the two subjects identified the stimulus correctly only approximately 44\% and 35\% of the time.

In the context of imitation of success in a game where states have a degree of similarity between them, the possibility of agents mistaking one state for another is thus something that should be taken into account.
Imitation dynamics could be affected by at least two sources of probabilistic noise:
